Capstone Movielens Report

### 2025-11-26 reports/capstone-movielens.site/02.5.UME-model.Rmd
Report: UME Model review.

  - [calc_user_movie_effect_RMSE.cv](#func.calc_user_movie_effect_RMSE.cv) (described in the [UME Model: Utility Functions] section) to calculate the *RMSE* for the *Current Model*;

  - [RMSEs.AddRow](#func.RMSEs.AddRow) and [RMSE_kable](#func.RMSE_kable) (described in the [Result RMSEs Tibble Functions] section) to update and print the table above.
:::

@@

UM_effect.loop_starter <- c(endpoints["start"], 
                            endpoints["end"], 
                            8)
UME.rglr.fine_tune.cache.base_name <- "UME.rglr.fine-tune"
```

@@

```{r}
print(UM_effect.loop_starter)
print(UME.rglr.fine_tune.cache.path)
print(UME.rglr.fine_tune.cache.base_name)
```
```{r, eval=FALSE}

@@

UME.rglr.fine_tune.RMSE.best <- UME.rglr.fine_tune.results$best_result["best_RMSE"]
```
```{r, echo=FALSE}
writeLines("*** Fine-tuning results object data structure ***")
```
```{r}
str(UME.rglr.fine_tune.results)
```
```{r, echo=FALSE}
writeLines("*** Fine-tuning: best results ***")
```
```{r}
UME.rglr.fine_tune.results$best_result
```

@@

Now, we can refine our _User+Movie Effect Model_ by retraining on the entire `edx` dataset with the best value of the $\lambda$ parameter we just figured out (let's call it *Regularized User+Movie Effect Model*), for the definitive _Root Mean Squared Error_ calculation and use in subsequent models.
```{r, eval=FALSE}
  UME.rglr.best_lambda <- best_result["param.best_value"]
  UME.rglr.best_lambda

@@

@@

We calculate the *RMSE* for the ultimately *Regularized User+Movie Effect Model* using [calc_user_movie_effect_RMSE.cv](#func.calc_user_movie_effect_RMSE.cv) function already used above in the [UME Model Building] section:
```{r, eval=FALSE}
UME.rglr.retrain.RMSE <- calc_user_movie_effect_RMSE.cv(rglr.UM_effect)
```
```{r}
print_log1("The best RMSE after being regularized: %1",
         UME.rglr.retrain.RMSE)
```

>>>>

  - [calc_user_movie_effect_RMSE.cv](#func.calc_user_movie_effect_RMSE.cv) (described in the *Models Training: Support Functions /* [UME Model: Utility Functions] section) to calculate the *RMSE* for the *Current Model*;

  - [RMSEs.AddRow](#func.RMSEs.AddRow) and [RMSE_kable](#func.RMSE_kable) (described in the *Common Helper Functions /* [Result RMSEs Tibble Functions] section) to update and print the table above.
:::

@@

UM_effect.loop_starter <- c(endpoints["start"], 
                            endpoints["end"], 
                            8)
```

@@

```{r}
UM_effect.loop_starter
UME.rglr.fine_tune.cache.path
```
```{r, eval=FALSE}
UME.rglr.fine_tune.cache.base_name <- "UME.rglr.fine-tune"

@@

UME.rglr.fine_tune.RMSE.best <- UME.rglr.fine_tune.results$best_result["best_RMSE"]
```
```{r, echo=FALSE}
writeLines("*** Fine-tuning results object data structure ***")
```
```{r}
str(UME.rglr.fine_tune.results)
```
```{r, echo=FALSE}
writeLines("*** Fine-tuning: best results ***")
```
```{r}
UME.rglr.fine_tune.results$best_result
UME.rglr.fine_tune.RMSE.best
```

@@

Now, we can refine our _User+Movie Effect Model_ by retraining on the entire `edx` dataset with the best value of the $\lambda$ parameter we just figured out (let's call it *Regularized User+Movie Effect Model*), for the definitive _RMSE_ calculation and use in subsequent models.
```{r, eval=FALSE}
best_result <- UME.rglr.fine_tune.results$best_result
UME.rglr.best_lambda <- best_result["param.best_value"]

@@

```{r}
```

@@

We calculate the *RMSE* for the ultimately *Regularized User+Movie Effect Model* using [calc_user_movie_effect_RMSE.cv](#func.calc_user_movie_effect_RMSE.cv) function (already used above in the [UME Model Building] section):
```{r, eval=FALSE}
UME.rglr.retrain.RMSE <- calc_user_movie_effect_RMSE.cv(rglr.UM_effect)
```
```{r}
print_log1("The best RMSE after being regularized: %1",
         UME.rglr.retrain.RMSE)
```
